SUPPLEMENTARY INFORMATION: NMRlipids III: Lipid-cholesterol interactions in atomistic resolution molecular dynamics simulations

### 2023-01-03 MANUSCRIPT/manuscriptSUPPL.tex

\begin{figure}[htb!]
    \centering
    \includegraphics[width=8.7cm]{../FIGS/firstmin.pdf}
    \caption{\label{SIfig:firstmin}%
    \textbf{Effecf of CHOL on the location of the first minima in the form factor.}
    The minima are extracted from the form factors (Fig.~\ref{SIfig:scattering}) from experiment and simulation with the \texttt{findpeaks} function in Matlab and interpolated to all CHOL concentrations.
    }
\end{figure}

>>>>

\begin{figure}[htb!]
    \centering
    \includegraphics[width=8.7cm]{../FIGS/ffminima.pdf}
    \caption{\label{SIfig:ffminima}%
    \textbf{Effecf of CHOL on the location of the first two minima in the form factor.}
    The minima are extracted from the form factors interpolated to all CHOL concentrations (Fig.~\ref{SIfig:scattering}) from experiment and simulation with the \texttt{findpeaks} function in Matlab.
    }
\end{figure}
